---
title: "Relatório 2: Análise Descritiva"
framework: bootstrap
mode: selfcontained
highlighter: prettify
bibliography: atlas.bib
csl: stat.csl
assets:
  css:
    - "http://fonts.googleapis.com/css?family=Raleway:300"
    - "http://fonts.googleapis.com/css?family=Oxygen"
output: html_document
---

<link href="https://fonts.googleapis.com/css?family=Raleway" rel="stylesheet">
<link href="https://fonts.googleapis.com/css?family=Oxygen" rel="stylesheet"> 

<style>
body{
  font-family: 'Oxygen', sans-serif;
  font-size: 16px;
  line-height: 24px;
   text-align: justify;
}

h1,h2,h3,h4 {
  font-family: 'Raleway', sans-serif;
}

.container { width: 1000px; }

h1.title {
   font-size: 36px;
}

h3 {
  background-color: #bcf1e5;
  text-indent: 10px;
  font-size: 22px;
  line-height: 40px;
}
h4 {
   font-weight: bold;
   text-color: #747222;
   font-size: 20px;
   line-height: 40px;
   border-bottom: 1px solid black;
}

g-table-intro h4 {
  text-indent: 0px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE, cache.lazy = FALSE)
library(lubridate)
library(magrittr)
library(tidyverse)
```

<br>

## Dados

```{r}
obrigacoes <- read_rds("../data/obrigacoes.rds")
pagamentos <- read_rds("../data/pagamentos.rds")
lim_saque  <- read_rds("../data/lim_saque.rds") 
lim_saque  <- read_rds("../data/lim_saque.rds") 
disponibilidades_liquidas_diarias <- read_rds("../data/disponibilidades_liquidas_diarias.rds")
disponibilidades_liquidas_diarias_visao_ug <- read_rds("../data/disponibilidades_liquidas_diarias_visao_ug.rds")
```

## Disponibilidade Líquida Diária

```{r}
disponibilidades_liquidas_diarias
```


